Learned image compression

### 2023-03-20 paper/paper.tex
Add Teemus results + authors contributions

@@

>>>>

Juha Ylikoski was responsible for creating the cnns around the SCCTX-model and training the networks. Teemu Eerola was responsible for creating the SCCTX model, forward pass and compression/decompression methods.
Nardos Estifanos was responsible for evaluation of the results.
All of us were partially responsible for the report for our corresponding parts.

@@

Like seen from the Fig. 2 our models performance in quantitative evaluation is worse than any conventional method apart from the JPEG in very low bitrates. The BD-SNR is -8.32 dB and BD-rate 3.84\% compared to JPEG. In calculations we used only JPEG compressors those \textit{bdd} were in the same range than our models. The comparison is not fear because the \textit{bdd} ranges are slightly different as discussed above. From our models, we can compare the performance of two models that were trained on $\lambda$=8e-4 by using the KODAK dataset \cite{kodak}. Other models are not comparable in with BD-rates because the range of \textit{bbp} are different. In terms of BD-rate we got 3.987\% from the model that was trained only 250 epochs and N=M=192 (Model 1) compared to the one trained for 300 epochs with N=128 and M=192 (Model 3) with yields that less trained model with more parameters performs better. This is reasonable since bigger model should have better quality even with bit less training.
